The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
rough p3, p4

### 2
<!--
* multilayer networks are new but folks have looked at habitat selection + sociality
  * Fortin
  * Banks
  * McLoughlin

@@

### 3
Scale + habitat selection and space use
types of scale to consider in these types of ML nets

@@

* Mayor et al. 2009 paper 
* MRSF Laforge paper 
* van Beest et al. 2014 scale paper 
* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
* Multi-scale habitat selection modeling: a review and outlook

### 4
how to combine moving forward
multilayer networks across landcover types
in areas of high selection/low selection or favorable/unfavorable habitat
combined with seasonality

@@

we could define layers of the multilayer network according to home range overlap 
instead of specific associations
looking at broader temporal scales and coarser spatial resolutions

>>>>

<!--
* multilayer networks are new but folks have looked at habitat selection + sociality
  * Fortin
  * Banks
  * McLoughlin

@@

<!--

Scale + habitat selection and space use
types of scale to consider in these types of ML nets

@@

* Mayor et al. 2009 paper 
* MRSF Laforge paper 
* van Beest et al. 2014 scale paper 
* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
* Multi-scale habitat selection modeling: a review and outlook
-->
Scale in habitat selection... Mayor (2019)

<!--
how to combine moving forward
multilayer networks across landcover types
in areas of high selection/low selection or favorable/unfavorable habitat
combined with seasonality

@@

we could define layers of the multilayer network according to home range overlap 
instead of specific associations
looking at broader temporal scales and coarser spatial resolutions
-->
How to combine moving forward: habitat selection, space use, multiple scales, multilayer networks
Sociality across scales eg home range overlap and interactions
Layers defined by habitat/landcover
